%=========================================================================
\documentclass[11pt,twoside,a4paper]{article}
\usepackage[english]{babel}
\usepackage{a4wide,times}
\title{Title of the Design}
\author{
Made by\\
Naam Student1, 3458923\\
Naam Student2, 3456738\\
\\
Specified by\\
Naam Student3, 3458966\\
Naam Student4, 3456706\\
}
\date{14 November 2014}
\begin{document}
\maketitle
\thispagestyle{empty}
\vspace{30 mm}
\begin{center}
\Large \bf 
Abstract
\end{center}
This document describes the contents a design report for the module assignment of the EPO-3 project. 
It can be used a template for writing this report. 
Here you should give a summary of the report.
\clearpage

\tableofcontents
\clearpage

\section{Introduction}
Tell something about the context of this report.

\section{Specification}
Give the literal design specification of the client.

\section{Design}
Describe how the specification of the design has been interpreted and how the design 
has been done, until the VHDL description.
\begin{itemize}
\item
Block description with inputs and outputs.
\item
Possible subdivision into sub-blocks.
\item
One or more Finite State Diagrams, if appropriate.
\item
VHDL behaviour description(s).
\end{itemize}

\section{Results}
Tell about the results:
\begin{itemize}
\item
Simulation results for the VHDL top-level description.
\item
Layout results.
\item
Switch-level/Spice simulation results for the extracted circuit.
\end{itemize}

\section{Conclusions}
Does the design meet the specifications?
Is there something that can be improved?

\begin{thebibliography}{9}
\bibitem{labelboek1}
Author1, 
Book1, 
Publisher, 
year.
\bibitem{labelTitel}
Author1, 
Title, 
Magazine, 
Vol. 1, 
Nr. 1, 
year, 
pp. 12-15.
\bibitem{labelWeb}
Webpages title, 
http link, 
accessed on 19 sep. 2013.
\end{thebibliography}
\end{document}
